---
title: "CO2 emissions by fuel "
author: 
  - Aanchal Dusija
  - Xiaojing Ni
format: html
embed-resources: true
code-fold: true
---
This notebook is the revised version of the pie chart. 

# Where do CO2 emissions come from?

Various fuel types can contribute to the carbon dioxide emissions linked to energy and industrial output. Each of these sources' contribution has evolved dramatically throughout time and continues to vary greatly by region. The graphic shows the absolute and relative contribution of CO2 emissions by source, broken down into cement manufacturing, gas flaring, oil flaring, and coal. By moving to the chart's "relative" mode, it is easiest to show that solid fuel use predominated early industrialization on a worldwide scale.

```{r global, include=FALSE}
#| echo: false
rm(list = ls())
# install.packages("streamgraph", repos = "http://cran.rstudio.com/")
# install.packages("devtools")
# devtools::install_github("hrbrmstr/streamgraph")
#library(streamgraph)
library(crosstalk)
library(htmlwidgets)
library(tidyr)
library(webshot)
library(plotly)
library(RColorBrewer)
library(inlmisc)
#if (!requireNamespace("remotes")) install.packages("remotes")
#remotes::install_github("USGS-R/inlmisc", dependencies = TRUE)

```

# Data

```{r}
df <- read.csv("../data/CO2-by-source.csv")
df<-df[,-2]
colnames(df) <- c("Country", "Year", "Others","Flaring","Cement","Gas","Oil","Coal")
head(df)
```

```{r}
df_long <- gather(df, key = "Type", value = "Value", -Country, -Year)
head(df_long)
```

# Graphing

```{r}
# US
df_us <- df_long[df_long$Country=="United States",]
head(df_us)

# CHINA
df_china <- df_long[df_long$Country=="China",]
head(df_china)

# BRAZIL
df_brazil <- df_long[df_long$Country=="Brazil",]
head(df_brazil)

# CANADA
df_canada <- df_long[df_long$Country=="Canada",]
head(df_canada)

# RUSSIA
df_russia <- df_long[df_long$Country=="Russia",]
head(df_russia)
```

```{r}
# group by fuel type and calculate total CO2 emissions
df_us_sum <- aggregate(df_us$Value, by=list(Category=df_us$Type), FUN=sum)



# group by fuel type and calculate total CO2 emissions
df_china_sum <- aggregate(df_china$Value, by=list(Category=df_china$Type), FUN=sum)


# group by fuel type and calculate total CO2 emissions
df_brazil_sum <- aggregate(df_brazil$Value, by=list(Category=df_brazil$Type), FUN=sum)



# group by fuel type and calculate total CO2 emissions
df_canada_sum <- aggregate(df_canada$Value, by=list(Category=df_canada$Type), FUN=sum)


# group by fuel type and calculate total CO2 emissions
df_russia_sum <- aggregate(df_russia$Value, by=list(Category=df_russia$Type), FUN=sum)


```

```{r}
library(plotly)
library(dplyr)

fig <- plot_ly(width = 800, height = 500)

### Brazil
fig <-
  fig %>% add_pie(
    data = df_brazil_sum,
    labels = ~ Category,
    values = ~ x,
    sort = FALSE, ## change the order manually
    hole = 0.6, 
    name = "Brazil",
    domain = list(x = c(0.063, 0.598), y = c(0.475, 0.95)),
    textposition = 'inside',
    insidetextfont = list(color = '#FFFFFF'),
    hoverinfo = 'label+percent',
    textinfo = 'label+percent',
    #marker = list(colors = inlmisc::GetTolColors(n =  length(df_russia_sum$Category)))
    marker= list(colors = c("#AADDCC","#78B9D2","#DDCC66","#CCDDAA","#BBCCEE","#FFCCCC"))

  )


### China
fig <-
  fig %>% add_pie(
    data = df_china_sum,
    labels = ~ Category,
    values = ~ x,
    sort = FALSE, ## change the order manually
    hole = 0.6,
    name = "China",
    domain = list(x = c(0.402, 0.937), y = c(0.475, 0.95)),
    textposition = 'inside',
    insidetextfont = list(color = '#FFFFFF'),
    hoverinfo = 'label+percent',
    textinfo = 'label+percent',
    marker= list(colors = c("#AADDCC","#78B9D2","#DDCC66","#CCDDAA","#BBCCEE","#FFCCCC"))

    # marker = list(colors = brewer.pal(
    #   n = length(df_russia_sum$Category), name = 'Greens'
    # ))
  )


## U.S.
fig <-
  fig %>% add_pie(
    data = df_us_sum,
    labels = ~ Category,
    values = ~ x,
    sort = FALSE, ## change the order manually
    hole = 0.6,
    name = "U.S.",
    domain = list(row = 1, column = 0),
    textposition = 'inside',
    insidetextfont = list(color = '#FFFFFF'),
    hoverinfo = 'label+percent',
    textinfo = 'label+percent',
    marker= list(colors = c("#AADDCC","#78B9D2","#DDCC66","#CCDDAA","#BBCCEE","#FFCCCC"))

    # marker = list(colors = brewer.pal(
    #   n = length(df_russia_sum$Category), name = 'Greens'
    # ))
  )


## Canada
fig <-
  fig %>% add_pie(
    data = df_canada_sum,
    labels = ~ Category,
    values = ~ x,
    sort = FALSE, ## change the order manually
    hole = 0.6,
    name = "Canada",
    domain = list(row = 1, column = 1),
    textposition = 'inside',
    insidetextfont = list(color = '#FFFFFF'),
    hoverinfo = 'label+percent',
    textinfo = 'label+percent',
    marker= list(colors = c("#AADDCC","#78B9D2","#DDCC66","#CCDDAA","#BBCCEE","#FFCCCC"))

    # marker = list(colors = brewer.pal(
    #   n = length(df_russia_sum$Category), name = 'Greens'
    # ))
  )


## Russia
fig <-
  fig %>% add_pie(
    data = df_russia_sum,
    labels = ~ Category,
    values = ~ x,
    sort = FALSE, ## change the order manually
    hole = 0.6,
    name = "Russia",
    domain = list(row = 1, column = 2),
    textposition = 'inside',
    insidetextfont = list(color = '#FFFFFF'),
    hoverinfo = 'label+percent',
    textinfo = 'label+percent',
    marker= list(colors = c("#AADDCC","#78B9D2","#DDCC66","#CCDDAA","#BBCCEE","#FFCCCC"))

    # marker = list(colors = brewer.pal(
    #   n = length(df_russia_sum$Category), name = 'Greens'
    # ))
  )


## layout
fig <-
  fig %>% layout(
    title = "CO<sub>2</sub> emission by fuel type",
    showlegend = T,
    grid = list(rows = 2, columns = 3),
    xaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    yaxis = list(
      showgrid = FALSE,
      zeroline = FALSE,
      showticklabels = FALSE
    ),
    
    ### add annotations
    annotations = list(
      list(
        x = 0.305,
        y = 0.805,
        text = "Brazil",
        "showarrow" = F,
        font = list(size = 12)
      ),
      list(
        x = 0.704,
        y = 0.805,
        text = "China",
        "showarrow" = F,
        font = list(size = 12)
      ),
      list(
        x = 0.083,
        y = 0.28,
        text = "United States",
        "showarrow" = F,
        font = list(size = 12)
      ),
      list(
        x = 0.503,
        y = 0.28,
        text = "Canada",
        "showarrow" = F,
        font = list(size = 12)
      ),
      list(
        x = 0.885,
        y = 0.28,
        text = "Russia",
        "showarrow" = F,
        font = list(size = 12)
      )
    ),
    
    ## add images
    images = list(
      ## Brazil
      list(
        source =  base64enc::dataURI(file = "../img/oil_pie.png"),
        xref = "paper",
        yref = "paper",
        x = 0.25,
        y = 0.747,
        sizex = 0.17,
        sizey = 0.17,
        layer = "below"
      ),
      ## China
      list(
        source =  base64enc::dataURI(file = "../img/coal.png"),
        xref = "paper",
        yref = "paper",
        x = 0.62,
        y = 0.747,
        sizex = 0.17,
        sizey = 0.17,
        layer = "above"
      ),
      ## U.S.
      list(
        source =  base64enc::dataURI(file = "../img/coal.png"),
        xref = "paper",
        yref = "paper",
        x = 0.1,
        y = 0.28,
        sizex = 0.17,
        sizey = 0.17,
        layer = "above"
      ),
      ## Canada.
      list(
        source =  base64enc::dataURI(file = "../img/oil_pie.png"),
        xref = "paper",
        yref = "paper",
        x = 0.42,
        y = 0.28,
        sizex = 0.17,
        sizey = 0.17,
        layer = "above"
      ),
      ## Russia
      list(
        source =  base64enc::dataURI(file = "../img/oil_pie.png"),
        xref = "paper",
        yref = "paper",
        x = 0.77,
        y = 0.28,
        sizex = 0.17,
        sizey = 0.17,
        layer = "above"
      )        
    )
  )

fig
saveWidget(fig, "fig.html", selfcontained = F, libdir = "lib_fig")

```

